\documentclass[a4paper, 12pt]{article}

% Configuration {{{
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc} % T1 for English
\usepackage[english]{babel}

\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{xcolor}
\definecolor{dimblue}{HTML}{1010aa}
\usepackage[
  colorlinks=true,
  allcolors=dimblue
]{hyperref}
\usepackage[
  %showframe,
  vmargin=1.8cm,
  hmargin=2cm
]{geometry}
\linespread{1.3}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[multidot]{grffile}
\usepackage[labelsep=period]{caption}
\usepackage{multirow}

%\usepackage{times} % for English

%\pagestyle{empty}
\setlength{\parindent}{0pt}

\def\mailto#1{\href{mailto:#1}{#1}}

\def\saneskip{.5\baselineskip}

\newcommand{\cvitem}[2]{
  \vskip .5\baselineskip
  \textbf{\large #1}
  \nopagebreak \vskip -.6\baselineskip
  \hrulefill
  \nopagebreak \vskip -.3\baselineskip #2
  %\parbox[t]{.2\linewidth}{\textsc{#1}}
  %\hfill
  %\parbox[t]{.7\linewidth}{#2}
}
% }}}

\usepackage{lipsum}

\begin{document}

% Name, contact information {{{
\parbox[c]{.5\linewidth}{\Large\bf Abdul-Kerim Guseinov}
\hfill \parbox[c]{.4\linewidth}{
  \flushright \vskip -.5\baselineskip
  %\mailto{guseynovkerim@gmail.com} \\
  \mailto{kerim.guseinov@cern.ch} \\
  Moscow, Russia \\
  +7 915 273 3700%
  \strut
}
%}}}

%\cvitem{Research Interests}{% Removed {{{
%  Particle physics, heavy flavor physics, hadron spectroscopy
%}%}}}

\cvitem{Education}{%{{{
  \begin{itemize}
    \item \textbf{Lomonosov Moscow State University}, Moscow, Russia
      \hfill Sep 2022 -- present
      \\ Postgraduate student,
      Faculty of~Physics, Department of General Nuclear Physics.
      %\\ Topic: \textit{\color{red} Some title or general words...}

    \item \textbf{Lomonosov Moscow State University}, Moscow, Russia
      \hfill Sep 2020 -- Jun 2022
      \\ M. Sc. in Physics, Department of General Nuclear Physics.
      \\ Thesis: \textit{Properties of multihadron decays of bottom 
      baryons produced in proton-proton collisions at the Large Hadron 
      Collider.}
      \\ Graduated summa cum laude: excellent grades throughout 
      the course of study.

    \item \textbf{Lomonosov Moscow State University}, Moscow, Russia
      \hfill Sep 2016 -- Jun 2020
      \\ B. Sc. in Physics, Department of General Nuclear Physics.
      \\ Thesis: \textit{Multiparticle hadronic decays of bottom baryons 
      produced in the LHCb detector.}
      \\ Graduated summa cum laude: excellent grades throughout 
      the course of study.

    \item \textbf{Lyceum N1586}, Moscow, Russia
      \hfill Grad. in Jun 2016
      \\ Specialized in Physics and Mathematics.
      \\ Graduated with distinction: grade average 5.0 of 5 in Grade 
      Certificate.
  \end{itemize}
}%}}}

\cvitem{Working Experience}{%{{{
  \begin{itemize}
    \item Laboratory Assistant at~the~Institute for~Theoretical 
      and~Experimental Physics (ITEP).
      \\ \null \hfill 2019 -- 2023
    \item Member of the LHCb research groups at ITEP and SINP MSU since 
      2019.
    %\item Member of an LHCb research group at SINP MSU since 2019.
    \item Primary author of LHCb-ANA-2015-020:
      First observation of the $\Lambda_b^0{\to}D^+p\pi^-\pi^-$ and 
      $\Lambda_b^0{\to}D^{*+}p\pi^-\pi^-$ decays.
      Paper published in~JHEP (see below).
      \\ My contribution: fitting model development and tuning, 
      estimation of~fitting model systematics,
      statistical experiments studies.
    \item Primary author of LHCb-ANA-2021-060:
      Study of charm baryon resonances in the 
      $\Lambda_b^0\to\Lambda_c^+\pi^+\pi^-\pi^-$ decay. (in preparation)
      \\ My contribution: development of~fitting models for~all relevant 
      spectra, fitter stabilization, measurements of~masses and~widths 
      of~baryon resonances, preliminary estimates of~systematics.
    \item Reported on~the~status of~the~analysis of~charm resonances in 
      $\Lambda_b^0\to\Lambda_c^+\pi^+\pi^-\pi^-$ at~B2OC Meetings 
      on~24~Nov~2022 and~15~Jun~2023.
      (\href{https://indico.cern.ch/event/1221243/%
      \#26-study-of-charm-baryons-in-l}{Indico page 1},
      \href{https://indico.cern.ch/event/1273384/%
      \#1-charm-baryon-resonances-in-l}{2})
  \end{itemize}
}%}}}

\cvitem{Conferences and Workshops}{%{{{
  \begin{itemize}
    \item 2nd Trans-Siberian School on High Energy Physics,
      organized by Tomsk Polytechnic University and CERN.
      \hfill \makebox{Apr 2019}
    \item 20th Interuniversity Concentrated Energy Flows Conference 
      organized by Lomonosov MSU:
      Preliminary results on~$\Lambda_b$~multihadron decays branching 
      ratios on~behalf of~the~LHCb Collaboration.
      \hfill \makebox{Nov 2019}
    \item 54th Winter School organized by PNPI in St. Petersburg.
      \hfill \makebox{Mar 2020}
    \item Lomonosov Universiade: Analysis of~fitting model systematics 
      and fit bias in~$\Lambda_b$ \textit{BR} measurements.
      \hfill \makebox{May 2020}
    \item 30th International Scientific Lomonosov Conference organized 
      by Lomonosov MSU:
      Preliminary results on~$\Lambda_b$~multihadron decay spectroscopy.
      %on~behalf of~the LHCb Collaboration.
      \hfill \makebox{Apr 2023}
  \end{itemize}
}%}}}

\cvitem{Publications}{%{{{
  \begin{itemize}
    \item % R. Aaij \textit{et al.} (LHCb Collaboration),
      LHCb Collaboration,
      Observation of $\Lambda_b^0{\to}D^+p\pi^-\pi^-$ and 
      $\Lambda_b^0{\to}D^{*+}p\pi^-\pi^-$ decays,
      \href{https://doi.org/10.1007/JHEP03(2022)153}
      {JHEP 03 153 (2022)}.
    \item A-K.\,D.~Guseinov, Measurement of~decays 
      $\Lambda_b^0{\to}D^+p\pi^-\pi^-$ and 
      $\Lambda_b^0{\to}D^{*+}p\pi^-\pi^-$ in~$pp$ collisions 
      at~the~Large Hadron Collider,
      \href{http://uzmu.phys.msu.ru/abstract/2020/2/2020301/}
      {Materials of~the~Faculty of~Physics of Lomonosov MSU, 2~(2020)}.
    \item A-K.\,D.~Guseinov \textit{et al.}, The Photon, ed. 
      Prof.~B.\,S.~Ishkhanov. Co-author of~a~book on~the~photon. 
      My~section is~concerned with~physical vacuum and Casimir effect. 
      (in~Russian)
      \href{http://dx.doi.org/10.31453/kdu.ru.91304.0112}
      {DOI: 10.31453/kdu.ru.91304.0112}.
      %{\color{red} move to activities?}
      %{\color{red} The only available link tries to sell a PDF version 
      %for 200 rub, but gives ISBN, DOI, etc.}
  \end{itemize}
}%}}}

\cvitem{Awards}{%{{{
  \begin{itemize}
    \item 6 times awarded the Increased State Academic Scholarship.
    \item 8 times awarded University Scholarships named after
      M.\,V.~Lomonosov, I.\,V.~Kurchatov, L.\,A.~Artsimovich, 
      R.\,V.~Khokhlov, and~S.\,I.~Vavilov.
    \item Was on~the~hall~of~fame at~the~Faculty of~Physics during 
      the~5th and~6th years at Lomonosov MSU.
    \item Trans-Siberian School on High Energy Physics visiting 
      fellowship.
  \end{itemize}
}%}}}

\cvitem{Teaching Experience}{%{{{
  \begin{itemize}
    \item Laboratory Instructor for 2nd year students practicum 
      on~Nuclear Physics.
      \\\null \hfill \makebox{Sep 2020 -- May 2021}
    \item Teaching Assistant, Mathematical analysis.
      \hfill Sep -- Dec 2017
    \item Teaching Assistant, Calculus. \hfill Jan -- Jul 2018
    \item {Many years of helping other students and answering their 
      meticulous questions about every course.}
  \end{itemize}
}%}}}

\cvitem{Software Experience}{%{{{
  \begin{itemize}
    \item Languages: C, C++, Python, Rust, Lua, Unix shells.
    \item Data analysis: ROOT, RooFit, PyROOT, Ostap.
    \item Other experience: Unix/Linux, Vim, Git, LaTeX.
  \end{itemize}
}%}}}

%\cvitem{Hardware Experience}{% Removed {{{
%  I don't have hardware experience yet, but I am very eager to acquire 
%  it and enthusiastic about such opportunities.
%  {\color{red} Move to the Motivation Letter}
%}%}}}

\end{document}
