\documentclass[a4paper, 12pt]{article}

% Configuration {{{
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian, english]{babel}

\usepackage[
	vmargin=1in,
	hmargin=1in
]{geometry}
\linespread{1.3}
\usepackage{xcolor}
\definecolor{allrefs}{HTML}{1010aa}
\usepackage[
	colorlinks=true,
	allcolors=allrefs
]{hyperref}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage[multidot]{grffile}
\usepackage[labelsep=period]{caption}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{mathtools}

%\usepackage{times}
\usepackage{multicol}
\usepackage{lipsum}
\setlength{\columnsep}{.25in}

\def\task#1{\begin{center}\it #1\end{center}}
\def\ans#1{\textit{#1}}

\newif\ifcols
\colsfalse
%}}}

\begin{document}

\noindent
Kerim Guseynov, 113M group
\hfill
Dec 11

\task{P. 93--95 (from meson factories), main thoughts}
% {{{
\par\textbf{\textit{Meson factories provide the answer.}}
The broken CP-symmetry may also be the reason to exist for the heavier 
generations of fundamental particles. Kobayashi and Maskava had 
predicted that B-mesons violate CP-symmetry, so their decays have been 
studied in detail. They indeed revealed the violation.

\textbf{\textit{Symmetry lies hidden under spontaneous violations.}}
The Standard Model describes three of the four fundamental forces of 
nature, but we haven't yet explained why they are so different. The 
reason is another broken symmetry. In physics, the vacuum is the lowest 
energy state of the system, and it doesn't have to be the most 
symmetric. The asymmetry between forces comes from our vacuum.

\textbf{\textit{Higgs provides mass.}}
It is commonly considered that a separate field called the Higgs field 
gives particles masses. In the early Universe, its state was symmetric, 
and all particles were massless. But as the Universe cooled down, the 
Higgs field decayed into its vacuum and started to differentiate 
particles. The Higgs boson, which represents the field, is now being 
sought at the largest accelerator in history --- LHC.
% }}}

\task{Ex. 1, p. 96}
% {{{
\textit{Broken symmetry} --- нарушенная симметрия.
\textit{Mirror symmetry} --- зеркальная симметрия.
\textit{Charge symmetry} --- зарядовая симметрия.
\textit{Time symmetry} --- симметрия обращения времени.
\textit{Conservation laws} --- законы сохранения.
\textit{The double CP-symmetry} --- двойная CP-симметрия.
\textit{Quarks} --- кварки.
\textit{B-mesons} --- B-мезоны.
\textit{Spontaneous symmetry violation} --- спонтанное нарушение симметрии.
\textit{The Higgs particle} --- частица Хиггса.
\textit{The Standard Model} --- Стандартная модель.
% }}}

\task{Ex. 2, p. 96}
% {{{
Because of classical physics and our everyday experience, we are used 
to \textit{nature's laws of symmetry}. But if it was translated to 
particle physics, there wouldn't be any \textit{excess of matter} over 
antimatter. At least \textit{a tiny deviation from perfect symmetry} is 
required at the early stages of the Universe. In classical physics, 
conservation laws help us \textit{simplify awkward calculations} and 
\textit{play a decisive role} in \textit{the mathematical description 
of the microworld}. To detect the small asymmetry, it is necessary to 
\textit{produce a constant stream of particles}. The Standard Model 
describes the \textit{indivisible parts of matter}. The excess of 
matter \textit{poses a challenge} to the theory behind the Standard 
Model. Modern accelerators can provide \textit{insights into the 
innermost parts of matter}. The quark mixing CP violation mechanism 
\textit{stands firmly on a theoretical base}. The Standard Model 
\textit{stood up to countless tests}, and now we almost don't know how 
to extend it. A Chinese experimental physicist Chien-Shiung Wu 
conducted an experiment to \textit{challenge mirror symmetry}. It 
appeared that we have to \textit{reevaluate old principles} in particle 
physics. After the P-symmetry was broken, physicists hoped that it's 
not possible to \textit{break the double CP-symmetry}. We should 
\textit{point out the importance of broken symmetry} --- it could 
\textit{set up conditions for} our cosmos to survive the first seconds 
after the Big Bang. The broken CP-symmetry lets us \textit{distinguish 
between matter and antimatter}. The amount of matter we have now had to 
\textit{originate in the heat of the Big Bang}, but the current 
theoretical deviation from CP-symmetry is not enough. The only source 
of CP violation in the Standard Model is \textit{the transformation of 
the quarks} also called quark mixing. To verify the suggestion of 
Kobayashi and Maskawa, we have to \textit{confirm the symmetry 
violation of the B-mesons}. As collider experiments went on, the 
Universe was found to \textit{be in accordance with the boldest 
predictions} of the Standard Model. Nambu realized that the same 
mechanism that makes superconductivity disappear could 
\textit{introduce spontaneous symmetry violation into elementary 
particle physics}. Physicists are now searching for evidence of new 
physics to \textit{extend the Standard Model} correctly and solve its 
major issues.
% }}}

\task{Ex. 3, p. 96}
% {{{
\begin{enumerate}[label=\alph*)]
	\item A tiny deviation from the perfect symmetry caused the excess of 
		matter over antimatter that we observe now.

	\item The three principles of symmetry are mirror symmetry, charge 
		symmetry, and time symmetry. They let us consider the behavior of 
		similar systems and test our understanding of the world.

	\item Deeper investigations into the world of elementary particles 
		made it possible to discover the structure of the proton and later 
		the neutron. This discovery was a large sign of the quark model.

	\item The strong force with its gluon, the electromagnetic force with 
		its photon, and the weak force with its W and Z bosons are 
		incorporated in the Standard Model. Gravity is not and is hence 
		challenging.

	\item Tsung Dao Lee and Chen Ning Yang challenged mirror symmetry by 
		suggesting an experiment with the weakly decaying cobalt-60. The 
		result was the discovery of P-symmetry violation.

	\item James Cronin and Val Fitch are famous for their experiment with 
		kaons that showed another symmetry breaking.

	\item Andrei Sakharov set up three conditions for creating a world 
		like ours. The laws of physics have to distinguish matter from 
		antimatter. The cosmos had to originate from the Big Bang. The 
		proton has to decay.

	\item A theoretical explanation for symmetry breaking was given by 
		Kobayashi and Maskava, with their idea of quark mixing 3x3 matrix.

	\item Two experiments, BaBar and Belle, also called b-factories, 
		confirmed B-meson mixing and hence CP violation.

	\item Yoichiro Nambu realized that the same mechanism that makes 
		superconductivity disappear could introduce spontaneous symmetry 
		violation. He suggested a theoretical source of such violation.

	\item The Standard Model has not yet been extended with anything. 
		Searches for new physics are still being conducted at the largest 
		and most expensive accelerator facilities in the history of 
		particle physics. Neither of the numerous possible extensions has 
		been confirmed.
\end{enumerate}
% }}}

\end{document}

New words:
- feasible -- осуществимый
