\documentclass[a4paper, 12pt]{article}

% Configuration {{{
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc} % T1 for English
\usepackage[russian, english]{babel}

\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{mathtools}
\usepackage{xcolor}
\definecolor{dimblue}{HTML}{1010aa}
\usepackage[
	colorlinks=true, 
	allcolors=dimblue
]{hyperref}
\usepackage[
	vmargin=1in,
	hmargin=1in
]{geometry}
\linespread{1.3}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage[multidot]{grffile}
\usepackage[labelsep=period]{caption}
\usepackage{subcaption}

%\usepackage{times} % for English
% }}}

\begin{document}

\noindent
Kerim Guseynov
\hfill
Mar 28

\begin{center}
	\textit{Ex. 1, p. 141, orally}
\end{center}

\begin{enumerate}[label=\alph*)]
	\item What kind of fields exist in quantum physics?

		There exist matter fields and force fields.

	\item Why is the Higgs field so important for the Standard Model?

		It is important because it produces masses of fundamental particles. Without it, everything would move at the speed of light.

	\item What is the difference between the Higgs field and other fields in physics?

		The difference is that the Higgs field never leaves the space-time completely, it is always there.

	\item How does the quantum mechanism discovered by F. Englert and P. Higgs provide a way for symmetry to both exist and be hidden from view at the same time?

		This mechanism involves a field that had a perfectly symmetric state immediately after the Big Bang but has then decayed to a lower energy state and lost its symmetry.

	\item How do the ATLAS and CMS detectors function?

		These detectors observe proton collisions at the LHC and try to register as much particles as possible. They are then combined to resolve the initial set of particles produced in the collision, some of which may be new to physics.

	\item Why is the Higgs particle not the final key to the Standard Model?

		There are other puzzles in physics that are not explained in the Standard Model. Some of them are masses of neutrinos and dark matter.
\end{enumerate}

\end{document}

- albeit - хотя
- stipulate - предусматривать
- primordial - исконный, первичный
- glimpse - взглянуть
- swarm - рой
