\documentclass[a4paper, 12pt]{article}

% Configuration {{{
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc} % T1 for English
\usepackage[russian, english]{babel}

\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{mathtools}
\usepackage{xcolor}
\definecolor{dimblue}{HTML}{1010aa}
\usepackage[
	colorlinks=true, 
	allcolors=dimblue
]{hyperref}
\usepackage[
	vmargin=1in,
	hmargin=1in
]{geometry}
\linespread{1.3}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage[multidot]{grffile}
\usepackage[labelsep=period]{caption}

%\usepackage{times} % for English

\def\ex#1{\begin{center}\textit{#1}\end{center}\vskip-.3\baselineskip}
% }}}

\begin{document}

\noindent
Kerim Guseynov, 113M
\hfill
Feb 10

\ex{Ex. 1, p. 107}
% {{{
   Charge-coupled device (CCD)~-- прибор с зарядовой связью (ПЗС).
\\ Optical amplifier~-- оптический усилитель.
\\ Optical waveguide technology~-- оптическая волноводная технология.
\\ Pixel~-- пиксель.
\\ Infrared light~-- инфракрасный свет.
\\ Bubble memory~-- магнитоэлектронное запоминающее устройство.
\\ Complementary Metal Oxide Semiconductor (CMOS)~-- комплементарная структура металл-оксид-полупроводник (КМОП).
\\ Continuous red light laser~-- непрерывный лазер красного света.
% }}}

\ex{Ex. 2, p. 107 (a--c)}
% {{{
\begin{enumerate}[label=\alph*)]
	\item
		   Сформировать современные информационные технологии -- to shape modern information technology.
		\\ Цифровой датчик изображения -- a digital image sensor.
		\\ Мгновенно получать информацию -- to instantly receive information.
		\\ Принимать что-то как должное -- to take something for granted.
		\\ Необходимое условие необычайно быстрого развития в области коммуникаций -- a prerequisite for the extremely rapid development in the field of communications.
		\\ Изменить условия в области фотографирования -- to alter the conditions for the field of photography.
		\\ Зафиксировать изображение в электронной форме при помощи датчика изображения -- to capture an image electronically with an image sensor.
		\\ Цифровая передача изображений -- digital transfer of images.
		\\ Способный передавать большие объемы информации -- capable of transferring large quantities of data.
		\\ Требовать многочисленных изобретений -- to require numerous inventions.

	\item
		   Бросить вызов воображению многих мужчин и женщин -- to challenge the imagination of many men and women.
		\\ Предоставить ответ -- to provide the answer.
		\\ Коэффициент преломления -- a refractive index.
		\\ Наметить путь промышленного производства медицинских инструментов -- to pave the way for industrial manufacturing of medical instruments.
		\\ Системы дальней связи -- long distance communication.
		\\ Удовлетворять растущие потребности в коммуникации -- to cover the growing communication needs.
		\\ Не принимать во внимание потенциал оптического света -- to disregard the potential of optical light waves.

	\item
		   Решительный шаг вперед к волоконной оптике -- a decisive stop forward for fiber optics.
		\\ Стабильный источник света -- a stable source of light.
		\\ Испускать интенсивный и строго направленный луч света -- to emit an intensive and highly focused beam of light.
		\\ Облегчить оптическую коммуникацию -- to facilitate optical communication.
		\\ Скрупулезно изучать что-либо -- to meticulously study something.
		\\ Представить свои заключения -- to present one's conclusions.
		\\ Упростить процесс -- to simplify the process.
		\\ Осуществимый, но крайне трудный -- feasible but very difficult.
\end{enumerate}
% }}}

\ex{Ex. 3, p. 109}
% {{{
\begin{enumerate}[label=\alph*)]
	\item It [glass] becomes strong, light, and flexible, which is 
		a \textit{prerequisite} if the fiber is to be buried, drawn under 
		water, or bent around corners.

	\item When \textit{voltage} is applied to the CCD array, the content 
		of the wells can be progressively read out.

	\item /.../ CCD \textit{breached} the limit of 100 megapixels, and 
		although the image quality is not dependent on the number of pixels, 
		\textit{surpassing} this limit is seen to have brought digital 
		photography a further step into the future.

	\item The electronic eye, the CCD, became the first truly successful 
		technology for the \textit{digital transfer of images}.

	\item During the production of glass, different additives such as 
		\textit{soda} and \textit{lime} are used to simplify the process.

	\item \textit{Notwithstanding} its bulky and primitive 
		characteristics, when compared to contemporary cameras, it initiated 
		a more commercially oriented digitization in the field of 
		photography.
\end{enumerate}
% }}}

\ex{Ex. 4, p. 109}
% {{{
\begin{enumerate}[label=\alph*)]
	\item True.
	\item False.
	\item False according to the text but true when considering 
		photoelectric effect in general (there could be any material as soon 
		as the light beam has high enough frequency and thus energy).
	\item False.
	\item False.
	\item False.
	\item True.
\end{enumerate}
% }}}

\ex{3-minute audiofile}

\end{document}

facilitate -- облегчить
meticulously -- скрупулезно
